Hydras \& Co.

### 2023-06-07 doc/chapter-fol.tex
more abbreviations

\inputsnippets{fol/depthDef,  FolExamples/DepthCompute}

@@

\inputsnippets{FolExamples/ltDepth1}

>>>>

\inputsnippets{fol/depthDef}

\begin{remark}
  The depth of a formula takes into account its abstract syntax tree \emph{with respect to the base connective and quantifiers : $\arrow$, $\sim$ and $\forall$}.
    Formulas which contain $\vee$, $\wedge$, $\exists$, etc. are translated into
    basic formulas before the computation of their depth. In the example below, 
the conjunction is translated into a bigger term than the disjunction.

\inputsnippets{FolExamples/DepthCompute}
\end{remark}

@@
